Constraining Quiescent Supermassive Black Hole Environments.

### 2014-09-04 ms.tex
Beginnings of angular momentum section.

\newcommand\lsim{\mathrel{\rlap{\lower4pt\hbox{\hskip1pt$\sim$}}
        \raise1pt\hbox{$<$}}}
\newcommand\gsim{\mathrel{\rlap{\lower4pt\hbox{\hskip1pt$\sim$}}
        \raise1pt\hbox{$>$}}}
\newcommand{\rs}{r_s}
\newcommand{\rb}{r_b}
\newcommand{\vw}{v_w}

@@

\begin{align}
\dot{M}=\frac{\eta \Menc(\rs)}{\rs}
\end{align}

@@

\[
\Lambda(T)\simeq
\begin{cases}
    2.3 \times 10^{-24} \left(T/10^6 \text{K}\right)^{0.5} $erg cm$^3 $s$^{-1}& \text{if } T \gsim 2 \times 10^7 \text{K} \\
    1.1 \times 10^{-22} \left(T/10^6 \text{K}\right)^{-0.7}  $erg cm$^3 $s$^{-1}& \text{if } T \lsim 2 \times 10^7 \text{K}     
\end{cases}
\label{eq:cooling}
\]

@@

\begin{figure}
\includegraphics[width=\columnwidth]{cooling.eps}
\caption{\label{fig:cooling} Ratio of heating ($H$) to cooling rate ($C$) for each of our solutions. The cooling rate is calculated using the approximate (solar metallicity) cooling function in Equation~\ref{eq:cooling}. The heating rate is estimated as $q \vw^2/2$. The ratio is computed assuming $eta=1$.}
\end{figure}

@@

\subsection{Angular Momentum}

\section{Summary}

>>>>

\newcommand\lsim{\mathrel{\rlap{\lower4pt\hbox{\hskip1pt$\sim$}}
        \raise1pt\hbox{$<$}}}
\newcommand\gsim{\mathrel{\rlap{\lower4pt\hbox{\hskip1pt$\sim$}}
        \raise1pt\hbox{$>$}}}
\newcommand{\rs}{r_s}
\newcommand{\rb}{r_b}
\newcommand{\rcirc}{r_{\rm circ}}
\newcommand{\rss}{r_{\rm ss}}
\newcommand{\lrs}{\l_{\rs}}
\newcommand{\lambdars}{\lambda_{\rs}}
\newcommand{\vw}{v_w}

@@

\begin{align}
\dot{M}=\frac{\eta \Menc(\rs)}{\th}
\end{align}

@@

\begin{align}
\Lambda(T)\simeq
\begin{cases}
    2.3 \times 10^{-24} \left(T/10^6 \text{K}\right)^{0.5} $erg cm$^3 $s$^{-1}& \text{if } T \gsim 2 \times 10^7 \text{K} \\
    1.1 \times 10^{-22} \left(T/10^6 \text{K}\right)^{-0.7}  $erg cm$^3 $s$^{-1}& \text{if } T \lsim 2 \times 10^7 \text{K}     
\end{cases}
\label{eq:cooling}
\end{align}

@@

\begin{figure}
\includegraphics[width=\columnwidth]{cooling.eps}
\caption{\label{fig:cooling} Ratio of heating ($H$) to cooling rate ($C$) for each of our solutions. The cooling rate is calculated using the approximate (solar metallicity) cooling function in Equation~\ref{eq:cooling}. The heating rate is estimated as $q \vw^2/2$. The ratio is computed assuming $\eta=1$.}
\end{figure}

@@

\subsection{Angular Momentum}
\label{sec:ang}
Our models are spherically symmetric and do not include the effects of
the gas' angular momentum. However, galaxies will in general have some
net rotation, and the gas will generally have some non-zero angular
momentum. At some radius, $\rcirc$, the specific angular momentum of
the gas will equal the specific angular momentum of a circular
orbit. Inside of this radius our assumptions of no rotation and
spherical symmetry will break down. But if $\rcirc$ inner sonic point
of the flow, the region where angular momentum becomes important will
be causally disconnected from the rest of the flow, and we would be
justified in neglecting angular momentum (at least on large scales).

The inner sonic point, $\rss$ general occurs at $\simq 1\%$ of
$\rinf$. $\rcirc$ depends on the gas injection radius. The largest
injection radius is $\rs$. Let $\lrs$ be the gas specific angular
momentum at $\rs$, then

\begin{align}
\rcirc=\frac{\lrs}{G \Mbh}
\end{align}

 used two-dimensional kinematic data to measure the ratio of ordered
 to random motion in a sample of early type galaxies. More precisely,
 they measure

\begin{align}
\lambda_R=\frac{\left<R|V|\right>}{\lef<R\sqrt{V^2+\sigma^2}\right>}
\end{align}

Where $R$ is the distance is the distance from the galactic center, $V$ is
the mean stellar velocity, and $\sigma$ is the velocity
disperison. The brackets represent a luminosity weighted average.

$\lrs\simeq\lambdars \sigma(\rs)^2 \rs^2$ 
\section{Summary}
